Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-01-29 alloscore_manuscript/alloscore-application-shorter.Rnw
updates and citations for data availability statement.

All forecast data used in this evaluation are available through the COVID-19 Forecast Hub \citep{cramer_reichlabcovid19-forecast-hub_2021}. An R package implementing the allocation score is available at \url{https://github.com/aaronger/alloscore} and all code for the analyses presented in this manuscript is available at \url{https://github.com/aaronger/utility-eval-papers}.

>>>>

All forecast data used in this evaluation are available through the COVID-19 Forecast Hub \citep{cramer_reichlabcovid19-forecast-hub_2021}. An R package implementing the allocation score is available at \url{https://github.com/aaronger/alloscore}. All code and data for the analyses presented in this manuscript are available at \url{https://github.com/aaronger/utility-eval-papers}. The analyses were generated using a reproducible workflow using \Sexpr{version$version.string} and the {\tt targets} package \citep{Rcore-2023, landau_2021_targets}.

### 2024-01-29 alloscore_manuscript/alloscore-application-shorter.tex
updates and citations for data availability statement.

All forecast data used in this evaluation are available through the COVID-19 Forecast Hub \citep{cramer_reichlabcovid19-forecast-hub_2021}. An R package implementing the allocation score is available at \url{https://github.com/aaronger/alloscore} and all code for the analyses presented in this manuscript is available at \url{https://github.com/aaronger/utility-eval-papers}.

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Jan 29 10:57:25 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

>>>>

All forecast data used in this evaluation are available through the COVID-19 Forecast Hub \citep{cramer_reichlabcovid19-forecast-hub_2021}. An R package implementing the allocation score is available at \url{https://github.com/aaronger/alloscore}. All code and data for the analyses presented in this manuscript are available at \url{https://github.com/aaronger/utility-eval-papers}. The analyses were generated using a reproducible workflow using R R version 4.3.2 (2023-10-31) and the {\tt targets} package \citep{Rcore-2023, landau_2021_targets}.

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Jan 29 11:09:55 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}
